Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-11-08 Thesis/chapter/04-experimental.tex
experiment fertig druebergelesen

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHARACTERISATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Characterisation}
All \gls{sem} micrographs were taken with a Zeiss Supra 40. 
\Gls{ft}\gls{uv}\gls{vis}\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident 
angle) were recorded with a Bruker Vertex 70 
%transmission [\%] and reflection?  which angle? 
spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and 
Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter} - \SI{588}
% gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
{\nano\meter}) and a Silicon detector for visual and \gls{ir} light 
(\SI{500}{\nano\meter} - \SI{1.2}{\micro\meter}). For transmittance the light
entered the sample from the side with the layer. The UV and VIS+IR spectra were merged 
in Opus software. % included in the spectrometer. 
\Gls{xrd} spectra were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer. 
All \gls{xrd} spectra were taken at \SI{5}{\degree} incident angle and compared to the internal database.

@@

\td{the choice of grenzen for \gls{doe} was done by biotic reinforcement learning (i.e. my brain)}
\td{Screening}

@@

using the Plackett-Burman \cite{Plackett1946} design implemented in the \texttt{python3} 

@@

relative concentration of Zr $c_{Zr}$, number of layers $n_{l}$, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} velocity $v_{DB}$[\mm{}/\s{}] and \gls{db} temperature $T_{DB}$[\oc{}], respectively. 

@@

			$c_{Zr}$	&$n_l$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\

@@

		\subcaption{Hand picked experiments}

@@

	4*	&6	&14	&60	&240	&500	\\
	4*	&6	&14	&60	&240	&500	\\
	4*	&6	&14	&60	&240	&500	\\

@@

%$T_{DB}$[\oc{}]
%$v_{DB}$[\mm{}/\s{}]
%$T_{cal}$[\oc{}]
%$v_{cal}$[\oc{}/\h{}]
%Especially the doctor blading velocity.
%}
%It was tried to reduce the waiting time and the resulting \td{drying stains}
%by using a heat gun. The drying was
%accelerated but not reproducibly and the glass plate on the film applicator was changed 
%against the heatable plate.
%With this new buthanolic recipe and heatable plate the limits of the optimization problem 
%were explored in a preliminary study using the Plackett-Burman \cite{Plackett1946} design 
%implemented in the \texttt{python3} library \texttt{pyDOE}.
%For the preliminary study a DB machine and NT were used and the steel. 
\ds{In the preliminary study only steel was used as substrate.}
%The Plackett-Burman \cite{Plackett1946} design implemented in the python3 library \texttt{pyDOE} was used to
%get an overview of reasonable boundaries.
%Latin squares were used to chose which experiments should be ausgefuehrt to get an ueberblick of the optimization room.
%See Code/Input_DOE/make_*exps.py and Code/Input_DOE/mail_theo
Some additional hand picked experiments (see table \ref{tab:pre-opt2}) were introduced to further narrow down the limits of 
the optimization as every reduction in variables or levels meant a faster convergence.
%ooooh 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Shortly before the \gls{pso} the stabilisation agent was changed from \gls{acoh} to 
\gls{ipo} because of much better solution stability.
The up to this moment best process was chosen to be tested with \ml{1} \gls{acoh}, \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} and \ml{1} \gls{ipo}.
%\td{As the sample showed the best all ex were proceeded with ipo as stabilatin agent. }
The sample produced with \gls{ipo} as stabilization agent showed comparable passivation results and better stability. Therefore \gls{ipo} was used  as stabilisation in further experiments.
After 
%a fitting recipe was found and 
the boundaries were fixed the process variables to 
produce an insulating layer was examined. 
%There were many variables which had to be taken into account. 
%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, DB velocity and DB temperature as input variables.}
See table \ref{tab:space} for the space spanned for the optimisation.
\begin{table}[ht!]
	\centering
	\caption{Final values used in the \gls{pso}.}
    \label{tab:space}
    \begin{tabular}{cccccc}
        \hline\hline
		$c_{Zr}$	&$n_l$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
%        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
        \hline
        2   &4  &10 &40 &120    &300    \\
        3   &6  &12 &50 &360    &400    \\
        4   &8  &14 &60 &600    &500    \\
        5   &10 &16 &70 &840    &       \\
            &12 &18 &80 &1080   &       \\
            &   &20 &   &       &       \\
        \hline\hline
    \end{tabular}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHARACTERISATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Characterisation}
All \gls{sem} micrographs were taken with a Zeiss Supra 40. 
\Gls{ft}\gls{uv}/\gls{vis}/\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident 
angle) were recorded with a Bruker Vertex 70 
%transmission [\%] and reflection?  which angle? 
spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and 
Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter} - \SI{588}
% gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
{\nano\meter}) and a Silicon detector for visual and \gls{ir} light 
(\SI{500}{\nano\meter} - \SI{1.2}{\micro\meter}). For transmittance the light
entered the sample from the side with the layer. The UV and VIS+IR spectra were merged 
in Opus software. % included in the spectrometer. 
\Gls{xrd} spectra were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer. 
All \gls{xrd} spectra were taken at \SI{5}{\degree} incident angle and compared to the internal database.

@@

%\td{the choice of grenzen for \gls{doe} was done by biotic reinforcement learning (i.e. my brain)}
%\td{Screening}
%The main part of the screening pre-optimisation samples were optimized via biotic reinforcement learning (i.e. my brain). 
The main part of all samples (around 90\%) were pre-optimization samples, 
from which the bulk were screening experiments optimized via biotic reinforcement learning 
(i.e. my brain) in order to obtain reasonable constraints for pre-optimization. 

@@

using the Plackett-Burman\cite{Plackett1946} design implemented in the \texttt{python3} 

@@

relative concentration of Zr $c_{zr}$, number of layers $\lambda$, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} velocity $v_{DB}$[\mm{}/\s{}] and \gls{db} temperature $T_{DB}$[\oc{}], respectively. 

@@

			$c_{zr}$	&$\lambda$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\

@@

        \subcaption{Hand picked experiments; $^*$varied stabilisation agent}

@@

	4$^*$	&6	&14	&60	&240	&500	\\
%	4$^\dagger$	&6	&14	&60	&240	&500	\\
%	4$^\ddagger$	&6	&14	&60	&240	&500	\\

@@

%$T_{DB}$[\oc{}]
%$v_{DB}$[\mm{}/\s{}]
%$T_{cal}$[\oc{}]
%$v_{cal}$[\oc{}/\h{}]
%Especially the doctor blading velocity.
%}
%It was tried to reduce the waiting time and the resulting \td{drying stains}
%by using a heat gun. The drying was
%accelerated but not reproducibly and the glass plate on the film applicator was changed 
%against the heatable plate.
%With this new buthanolic recipe and heatable plate the limits of the optimization problem 
%were explored in a preliminary study using the Plackett-Burman \cite{Plackett1946} design 
%implemented in the \texttt{python3} library \texttt{pyDOE}.
%For the preliminary study a DB machine and NT were used and the steel. 
\ds{In the preliminary study only steel was used as substrate.}
%The Plackett-Burman \cite{Plackett1946} design implemented in the python3 library \texttt{pyDOE} was used to
%get an overview of reasonable boundaries.
%Latin squares were used to chose which experiments should be ausgefuehrt to get an ueberblick of the optimization room.
%See Code/Input_DOE/make_*exps.py and Code/Input_DOE/mail_theo
Some additional hand picked experiments (see table \ref{tab:pre-opt2}) were introduced to further narrow down the limits of 
the optimization as every reduction in variables or levels meant a faster convergence.
%ooooh 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Shortly before the \gls{pso} the stabilisation agent was changed from \gls{acoh} to 
\gls{ipo} because of much better solution stability.
The - up to this moment - best process was chosen to be tested with 
\ml{1} \gls{acoh}, \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} and \ml{1} \gls{ipo}.
%\td{As the sample showed the best all ex were proceeded with ipo as stabilisation agent. }
The sample produced with \gls{ipo} as stabilization agent 
showed comparable passivization results and better stability. 
Therefore \gls{ipo} was used  as stabilisation in further experiments.
After the boundaries of the solution were fixed 
the process variables to produce an insulating layer was examined. 
%There were many variables which had to be taken into account. 
%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, DB velocity and DB temperature as input variables.}
See table \ref{tab:space} for the space spanned for the optimisation.
\begin{table}[ht!]
	\centering
	\caption{Final values used in the \gls{pso}.}
    \label{tab:space}
    \begin{tabular}{cccccc}
        \hline\hline
		$c_{zr}$	&$\lambda$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
%        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
        \hline
        2   &4  &10 &40 &120    &300    \\
        3   &6  &12 &50 &360    &400    \\
        4   &8  &14 &60 &600    &500    \\
        5   &10 &16 &70 &840    &       \\
            &12 &18 &80 &1080   &       \\
            &   &20 &   &       &       \\
        \hline\hline
    \end{tabular}
\end{table}

### 2022-11-08 Thesis/chapter/05-computational-details.tex
experiment fertig druebergelesen

\subsection{Data Processing}
\label{sec:eval}
Reading list
\begin{itemize}
    %\item https://de.wikipedia.org/wiki/Globaler_F-Test
    %\item https://de.wikipedia.org/wiki/Optimale_Versuchsplanung
    %\item Curse of dimensionality scholar
    %\item linear regression von ungar 
    %\item ridge regression + support vector machine
    %\item correlation vs covariance
    %\item https://en.wikipedia.org/wiki/Regression_analysis
    %\item https://en.wikipedia.org/wiki/Noise_reduction
    %\item https://en.wikipedia.org/wiki/Feature_extraction
    %\item https://en.wikipedia.org/wiki/Feature_selection
    %\item https://en.wikipedia.org/wiki/Dimensionality_reduction
    %\item file:///home/pur/Doc/Uni/Chemie_Master/Int_AIT/Int.git/Code/ML/98_things_can_go_wrong_in_ML_project.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.PCA.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.KernelPCA.html#sklearn.decomposition.KernelPCA
    \item 
    \item 
    \item 
\end{itemize}
%\td{describe problem and solution found}
For every sample multiple \gls{iv} curves were measured. 
The main difficulty faced in processing the data was to present the measurements obtain 
from a sample in one representative number. 
The average of each conductance would be an obvious choice but difficult to represent a 
sample correctly since the possible values of conductance span accross several magnitudes.
So the average of logarithms of conductances is the next nearby ansatz.
\todo{why didn't i just take this?}
\td{L2 norm because it might be easier to compare to other methods. }
\td{inspired by euclidean norm/L2 distance from ideal case} 
\td{wanted to put more weight on bad shunts}
\td{plot avg, avg(log), avg(log-13)}

For every I-V curve (aluminium dot) the gradient $g$ at $V=0$ is calculated by taking 
each $n=5$ points after and before the origin at least $d=2$ points distance (which boils
down to the values from \SI{0.02}{\volt} to \SI{0.07}{\volt}) , averaging their V and I values 
and calculating
\begin{equation}
    g = \frac{I_{+m+d} - I_n}{V_{n+1} - V_n}.
\end{equation}
As a measure of conductance a distance D from an ideal non-conducting case. The average of the negative base 10 logarithm subtracted from an ideal non-conducting gradient of $10^{-13}$ 
\begin{equation}
	D = \sum_i^N \frac{ -log_{10}(g_i) - 13}{N}
	\label{eq:D}
\end{equation}
Another measure is the density of shorted species $\rho_{s}$ is calculated in following way:
\begin{equation}
	s_i = \begin{cases}
	1 &\text{if} \quad -log(g_i) < 5 \\
	0 &\text{if} \quad -log(g_i) \geq 5 \\
	\end{cases}
\end{equation}
\begin{equation}
	\rho_s = \sum_i^N \frac{s_i}{N}
	\label{eq:rho}
\end{equation}
Other estimates of the conductance are the averages:
\begin{equation}
	G_1 = log \left( \sum_i^N \frac{g_i}{N} \right)
\end{equation}

\begin{equation}
	G_2 =  \sum_i^N \frac{log(g_i)}{N}
\end{equation}

\subsection{Sample Selection}
\label{sec:ss}
An evolutionary approach was chosen, namely a multi-objective Particle Swarm Optimization (PSO) with a multi-response
Multivariate Adaptive Regression Splines (MARS) model\cite{Villanova2010,Kennedy1995,Breiman1997,Carta2011}.
%
"PSO is a population based heuristic inspired by the flocking behavior of birds. 
To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{Villanova2010}
%
Initially the input parameters (independent variables), their boundaries and number of equidistant levels for each parameter are declared (see table \ref{tab:input}).
Next, the output variables (dependant variables), their weights in the objective function (the function which should be optimized) are specified and if they should be minimized or maximized is noted.
%
%An initial population of particles, i.e. experiments with certain parameters, is chosen out of the population space (space spanned by all possible combinations of input parameters), 
\begin{table}[htb]
	\centering
	\begin{tabular}{cc cc cc}
		\hline
		Zr(PrO)$_4$ conc. [21 g/L]	&layers	&$T_{DB}$[\oc{}]	&$v_{DB}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
		\hline
		2				&4		&40					&10				&300				&120	\\
		3				&6		&50					&12				&400				&360	\\
		4				&8		&60					&14				&500				&600	\\
		5				&10		&70					&16				&					&840	\\
						&12		&80					&18				&					&1080	\\
						&		&					&20				&					&		\\
		\hline
	\end{tabular}
	\caption{Discrete levels of each input parameter \td{are concentrations correct?}}
	\label{tab:input}
\end{table}

The first step is to select an initial population (ensemble of experiments), which is chosen randomly from the population space. 
The samples are made, measured and evaluated according to section \ref{sec:exp} and the distance $D$ (see eq. \ref{eq:D}), $\rho_s$ (see eq. \ref{eq:rho}), $n_{layers}$ (numbers of layers) and $v_{cal}$ (heating rate of calcination process in \oc{}/\minutes{}) are supplied to the program. 
The program uses this data to estimate a response for each output variable (and to choose a fraction of the initial population which is allowed to propagate).
The response variables for the entire population space is calculated. 
The current population - each of the particles independently - moves towards the optimum solution.
The population for the next time step is outputted and the experiments are again executed, measured and evaluated.

>>>>

\subsection{Data Processing}
\label{sec:eval}
%Reading list
%\begin{itemize}
    %\item https://de.wikipedia.org/wiki/Globaler_F-Test
    %\item https://de.wikipedia.org/wiki/Optimale_Versuchsplanung
    %\item Curse of dimensionality scholar
    %\item linear regression von ungar 
    %\item ridge regression + support vector machine
    %\item correlation vs covariance
    %\item https://en.wikipedia.org/wiki/Regression_analysis
    %\item https://en.wikipedia.org/wiki/Noise_reduction
    %\item https://en.wikipedia.org/wiki/Feature_extraction
    %\item https://en.wikipedia.org/wiki/Feature_selection
    %\item https://en.wikipedia.org/wiki/Dimensionality_reduction
    %\item file:///home/pur/Doc/Uni/Chemie_Master/Int_AIT/Int.git/Code/ML/98_things_can_go_wrong_in_ML_project.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.PCA.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.KernelPCA.html#sklearn.decomposition.KernelPCA
%    \item 
%\end{itemize}
%\td{describe problem and solution found}
For every sample multiple \gls{iv} curves were measured. 
The main difficulty faced in processing the data was to present the measurements obtain 
from a sample in one representative number. 
%
%\todo{why didn't i just take this?}
%\td{L2 norm because it might be easier to compare to other methods. }
%\td{inspired by euclidean norm/L2 distance from ideal case} 
%\td{wanted to put more weight on bad shunts}
%\td{plot avg, avg(log), avg(log-13)}
%
For every I-V curve (aluminium dot) the gradient $g$ at $V=0$ is calculated by taking 
each $n=5$ points after and before the origin at least $d=2$ points distance (which boils
down to the values from \SI{0.02}{\volt} to \SI{0.07}{\volt}), 
averaging their V and I values and calculating
\begin{equation}
    g = \frac{I_{+m+d} - I_n}{V_{n+1} - V_n}.
\end{equation}
%
The average of each conductance would be an easy and naive choice but difficult to represent a 
sample correctly since the possible values of conductance span across several magnitudes.
So the average of base 10 logarithm of conductances is the next nearby \textit{ansatz}.
%
In order to make the metric closer and better comparable to the \gls{mse} the average of the squared difference 
to the ideal non-conduction case ($g=10^{-13}$) was chosen instead of the average of logarithms. 
%As a measure of conductance a distance $D$ from an ideal non-conducting case. 
%The average of the negative base 10 logarithm subtracted from an ideal non-conducting gradient of $10^{-13}$ 
%and the mean of all conductances was taken
%
\begin{equation}
    \gamma = \sum_i^N \frac{ (-log_{10}(g_i) - 13)^2}{N}
	\label{eq:gamma}
\end{equation}
Another measure is the density of shorted species $\rho$, calculated in following way:
\begin{equation}
	s_i = \begin{cases}
	1 &\text{if} \quad -log(g_i) < 5 \\
	0 &\text{if} \quad -log(g_i) \geq 5 \\
	\end{cases}
\end{equation}
\begin{equation}
	\rho = \sum_i^N \frac{s_i}{N}
	\label{eq:rho}
\end{equation}
%Other estimates of the conductance are the averages:
%\begin{equation}
%	G_1 = log \left( \sum_i^N \frac{g_i}{N} \right)
%\end{equation}
%
%\begin{equation}
%	G_2 =  \sum_i^N \frac{log(g_i)}{N}
%%\end{equation}

\subsection{Sample Selection}
\label{sec:ss}
An evolutionary approach was chosen, namely a multi-objective 
\gls{pso} algorithm called \gls{emma}\cite{villanova2010function,Kennedy1995,Breiman1997,Carta2011}.
%
%"PSO is a population based heuristic inspired by the flocking behavior of birds. 
%To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{villanova2010function}
%
Initially, the input parameters (independent variables), their boundaries and number of equidistant levels for each parameter are declared (see table \ref{tab:input}).
Next, the output variables (dependant variables), their weights in the objective function (the function which should be optimized) are specified and if they should be minimized or maximized is noted.
%
%An initial population of particles, i.e. experiments with certain parameters, is chosen out of the population space (space spanned by all possible combinations of input parameters), 
\begin{table}[htb]
	\centering
	\begin{tabular}{cc cc cc}
		\hline
        $c_{zr}$ [21 g/L]	&$\lambda$	&$T_{DB}$[\oc{}]	&$v_{DB}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
		\hline
		2				&4		&40					&10				&300				&120	\\
		3				&6		&50					&12				&400				&360	\\
		4				&8		&60					&14				&500				&600	\\
		5				&10		&70					&16				&					&840	\\
						&12		&80					&18				&					&1080	\\
						&		&					&20				&					&		\\
		\hline
	\end{tabular}
	\caption{Discrete levels of each input parameter \td{are concentrations correct?}}
	\label{tab:input}
\end{table}

The \textit{optimizands} where chosen to be $\gamma$, $\rho$, $\lambda$ and $v_{cal}$, which all should be minimized except $v_{cal}$.
The next step is to select an initial population (ensemble of experiments), which is chosen randomly from the population space. 
The experiments are executed, measured and evaluated according to section \ref{sec:exp} and $\gamma$ (see eq. \ref{eq:gamma}), $\rho_s$ (see eq. \ref{eq:rho}), $n_{layers}$ (numbers of layers) and $v_{cal}$ (heating rate of calcination process in \oc{}/\minutes{}) are supplied to the program. 
\td{The program, then, uses this data to estimate a response for each output variable (and to choose a fraction of the initial population which is allowed to propagate).
The response variables for the entire population space is calculated. 
}
The current population - each of the particles independently - moves towards the optimum solution.
The population for the next time step is outputted and the experiments are again executed, measured and evaluated.
